% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Is crowdfunding having a negative effect on the games industry? If so is there a way for this be avoided? } 

% Please do not change the subtitle
\subtitle{COMP230 - Ethics and Professionalism}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\section{Proposal}

The topic I intend to research is on the issues of crowdfunding and how this method of funding effects game projects. This paper will try and  compare how successful crowdfunding is compared to traditional publishers, and how it effects the developers and the quality of the game. 



\subsection{Paper One:}

Kickstarter As a Source of Funds for Computer Games
\cite{Harris:2013}

\textbf{Notes:}

This paper states that while it is too early to makde definate judgemets kickstarter is not a viable alternative to traditional publishers.

Of the 468 projects analyzed, only 129(27percent) have delivered their game as of 2013.

Occasionally, a game must change features or otherwise break a promise made during funding, 
and there is not yeta clearly understood set of obligations between creators and backers for how this situation should be handled.


\subsection{Paper Two:}

Public Online Failure With Crowdfunding
\cite{Greenberg:2015}

The majority of projects on kickstarter fail. This paper focuses on public embarrasment in the process of running a kickstarted project.

This issue is important to ethics because having a project be a public embarrasment impacts the developers of that game.


\subsection{Paper Three:}

Show me the money!: an analysis of project updates during crowdfunding campaigns
\cite{xu2014show}

This paper tries to understand the factors that affect a kickstarter campaign.

They found that specific uses of updates had stronger associations with campaign success than the project’s description.

They desgined formulas from the results to help designers better support various uses of updates in crowdfunding campaigns.

Updates are critical to the success of a campaign.

the chance of success of a project without an update was only 32.6percent.

\subsection{Paper Four:}

A Long-Term Study of a Crowdfunding Platform: Predicting Project Success and Fundraising Amount
\cite{Chung:2015}
\textbf{Notes:}
This paper looks into what makes a crowdfunding project successful

\subsection{Paper Five:}

Recommending Investors for Crowdfunding Projects
\cite{An:2014}

\textbf{Notes:}
This paper has a lot of information about the financials of kickstarter.

\subsection{Paper Six:}

Crowdfunding Support Tools: Predicting Success and Failure
\cite{Greenberg:2013}

\textbf{Notes:}
This paper provides information about what works in planning a kickstarter. 

\subsection{Paper Seven:}
Crowdfunding creative ideas: The dynamics of project backers in Kickstarter
\cite{kuppuswamy2015}

\textbf{Notes:}
This article focuses on the funding that kickstarted projects get, and the ``U'' curve pattern that is associated with it.

\subsection{Paper Eight:}
The backer–developer connection: Exploring crowdfunding's influence on video game production
\cite{smith2014}

\textbf{Notes:}
As video game development studios increasingly turn to digital crowdfunding platforms such as Kickstarter for financing, this article explores the ways in which these processes shape production.

\subsection{Paper Nine:}
Crowdfunding: A new media and society special issue
\cite{bennett2014}

\textbf{Notes:}
This paper ties to unravel the developments and challenges involved in these processes of crowdfunding.



\bibliographystyle{ieeetr}
\bibliography{comp230_Ethics}

\end{document}
