\documentclass{beamer}
\usepackage{etoolbox}\newtoggle{printable}\togglefalse{printable}
\usetheme{Copenhagen}
\usepackage{listings}
\usepackage{algpseudocode}

\title{Is crowdfunding having a negative effect on the games industry? If so is there a way for this be avoided?}
\author{Alastair Rayner}
\date{\today}

\begin{document}

\maketitle

\begin{frame}{Proposal}
	\begin{itemize}
	\pause
		\item The topic I intend to research is on the issues of crowdfunding and how this method of funding effects game projects. This paper will try and  compare how successful crowdfunding is compared to traditional publishers, and how it effects the developers and the quality of the game.  \pause
	\end{itemize}
\end{frame}

\begin{frame}{Paper One}
	\begin{itemize}
		\item Kickstarter As a Source of Funds for Computer Games \pause
			\begin{itemize}
				\item This paper states that while it is too early to makde definate judgemets kickstarter is not a viable alternative to traditional publishers. \pause
				\item Of the 468 projects analyzed, only 129(27percent) have delivered their game as of 2013. \pause
				\item Occasionally, a game must change features or otherwise break a promise made during funding, 
and there is not yeta clearly understood set of obligations between creators and backers for how this situation should be handled. \pause
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Paper Two}
	\begin{itemize}
		\item Public Online Failure With Crowdfunding \pause
			\begin{itemize}
				\item The majority of projects on kickstarter fail. This paper focuses on public embarrasment in the process of running a kickstarted project. \pause
				\item This issue is important to ethics because having a project be a public embarrasment impacts the developers of that game.\pause
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Paper Three}
	\begin{itemize}
		\item The backer–developer connection: Exploring crowdfunding's influence on video game production \pause
			\begin{itemize}
				\item As video game development studios increasingly turn to digital crowdfunding platforms such as Kickstarter for financing, this article explores the ways in which these processes shape production. \pause
			\end{itemize}
	\end{itemize}
\end{frame}


\end{document}
